### 2017-04-03 paper/modes.tex
adjusting examples

\Fix{unconvincing.  please, revise this.$\rightarrow$}Considering efficiency, the
configuration \SeqClassParMeth{} may speedup the execution of test
suites composed of large test classes since the cost of running all
test methods is amortized by a pool of threads\Mar{$\leftarrow$
  unclear to me.  you need to argument why one would prefer C1 over
  C2.}. Similarly, the configuration \ParClassSeqMeth{} may speedup
test suites composed by several small test classes.\Mar{$\leftarrow$
  again, unclear to me (the reader).}  Finally, the configuration
\ParClassParMeth{} does not impose any sequential execution but it is
more likely to manifest data-races as methods from different classes
run in parallel.

>>>>

Considering efficiency, the configuration \SeqClassParMeth{} may
speedup the execution of test classes composed of small test methods
involving variables that is visible within the scope of the method.
Similarly, the configuration \ParClassSeqMeth{} may speedup
test suites composed by several test classes with few test methods.
Finally, the configuration \ParClassParMeth{} does not impose any 
sequential execution but it is more likely to manifest data-races as 
methods from different classes run in parallel.
